Effective workflow in molecular dynamics simulations using Atomify --- a real-time LAMMPS visualizer

### 2018-11-04 IOPLaTeX.tex
malthe is in the loop yo!
stuff

\author{Svenn-Arne Dragly$^{1}$}
\ead{s.a.dragly@fys.uio.no}
\address{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway}

@@

Fluid flow in porous structures is often characterized by its permeability, $k$, which describes the fluid flow conductivity of a fluid in a specific geometry. Darcy's law relates the average flow velocity, $U$, to the applied pressure gradient $\nabla P$: $U = (k/\mu)(-\nabla P)$, where $\mu$ is the viscosity of the fluid. In Darcy's law, the permeability is assumed to only depend on the material and its geometry. 
\todo[inline]{U is the flux here, not the average velocity?}
However, Darcy's law must be modified for dilute
gases where the measured permeability also is found to also be a function of pressure.
This is called the Klinkenberg effect\cite{klinkenberg1941permeability}.

>>>>

\author{Svenn-Arne Dragly$^{1}$}
\ead{s.a.dragly@fys.uio.no}

\author{Anders Malthe-S\o renssen$^{1}$}
\ead{malthe@fys.uio.no}
\address{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway}

@@

Fluid flow in porous structures is often characterized by its permeability, $k$, which describes the fluid flow conductivity of a fluid in a specific geometry. Darcy's law relates the fluid flux, $q$, to the applied pressure gradient $\nabla P$: $q = (k/\mu)(-\nabla P)$, where $\mu$ is the viscosity of the fluid. In Darcy's law, the permeability is assumed to only depend on the material and its geometry. 
\todo[inline]{U is the flux here, not the average velocity?}
However, Darcy's law must be modified for dilute
gases where the measured permeability also is found to also be a function of pressure.
This is called the Klinkenberg effect\cite{klinkenberg1941permeability}.
